---
title: "Title of Slides"
subtitle: "Lecture $n$ - CODE10001"

# Template file for using Quarto to create a COL-branded presentation. Released
# by Josh Fogg under a Creative Commons Zero (CC0) license.
---

## Placeholder

This slide is split into two columns, one with a list and one with an image from the web.

::::{layout-ncol=2 style="margin-top: 2em;"}
:::{style="font-size: 150%;"}
1. List item A,
2. List item B,
3. List item C,
4. Final list item.
:::

![[xkcd.com/1725](https://xkcd.com/1725/), Randall Munroe (2016) [CC BY-NC 2.5](https://creativecommons.org/licenses/by-nc/2.5/).](https://imgs.xkcd.com/comics/linear_regression.png){fig-alt="Two square panels show identical sets of scattered black dots, with only the red additions being different. The left panel shows a slightly rising red line drawn through the middle of the panel, passing near a few dots but not obviously related to most of them. A red text is below the dots: R-squared = 0.06. The right panel shows many of the dots connected by red lines to form a stick figure of a man resembling the constellation Orion, with the hand on the reader's right raised and holding an object. A red text is below the dots: Rexthor, the Dog-Bearer. A caption is below and spanning both panels: I don't trust linear regressions when it's harder to guess the direction of the correlation from the scatter plot than to find new constellations on it."}
::::

. . .

To access the speaker notes for these slides, tap `s` on your keyboard.

. . .

To export the slides, tap `e` and then print to PDF.

<!-- 
  If there's anything you want the teacher to know, but that shouldn't be in the
  speaker notes (which students can see!) it can go in block HTML comments.
-->

:::{.notes}
An example of an initial slide that might be used to give the overview of a presentation or a lecture. The image included shows the difference between an image caption (that everyone sees) and the image alt-text that accessibility tools will surface.
:::


# Example Section {.center background-color="#041E42" style="color: #d6d6d6; text-align: center;"}

:::{.notes}
Sections can be used to break up larger presentations.
:::

## Maths

Equations are formatted with $\mathrm{\LaTeX}$, either inline with `$...$` or centred with `$$...$$`.

::::{layout="[ [1], [1,1] ]"}
:::{.callout title="Theorem: Quadratic Equation"}
If $ax^2 + bx + c = 0$ where $a\neq0$, then the solutions are given by $x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}$.
:::

:::{.callout-tip title="Proof"}
\begin{align}
          ax^2 + bx + c &= 0 \\
  4a^2 x^2 + 4abx + 4ac &= 0 \\
  4a^2 x^2 + 4abx + b^2 &= b^2 - 4ac \\
          {(2ax + b)}^2 &= b^2 - 4ac \\
                2ax + b &= \pm\sqrt{b^2 - 4ac} \\
                   2ax  &= -b\pm\sqrt{b^2 - 4ac} \\
                     x  &= \frac{-b\pm\sqrt{b^2 - 4ac}}{2a} \\
\end{align}
:::

:::{.callout-note}
This is [Śrīdhara](https://en.wikipedia.org/wiki/Sridhara)'s method. The steps of the derivation are:

1. Multiply both sides by $4a$.
2. Add $b^2 - 4ac$ to both sides.
3. Complete the square on the left hand side.
4. Take the square root of both sides.
5. Subtract $b$ from both sides.
5. Divide both sides by $2a$ (since $a\neq0$).
$\square$
:::
::::

:::{.notes}
This example shows a combination of inline and display mode maths, include use of the `align` environment. The more complicated layout setting allows for two-column proofs. 
:::

## Nice Plots

Given response $y$ and **single** predictor $x$, this model fits to the equation

\begin{equation}
  y = \beta_{0} + \beta_{1}x.
\end{equation}


Visually, the line of best fit from linear regression may look like the below.

```{r}
#| label: scatter-plot
#| echo: false
#| out-width: '80%'
#| fig-align: 'center'
#| fig-format: svg
#| fig-alt: "Scatter diagram for the classic 'mtcars' dataset, showing miles per gallon against horsepower. A linear regression of y = 30 - 0.068x is shown."

library(ggplot2)  # standard package for making nice plots
library(ggpubr)   # annotations like stat_regline_equation

ggplot(mtcars, aes(x=hp, y=mpg)) +
  # plot the data
  geom_point(size=4, alpha=0.33, color="blue") +
  geom_smooth(formula=y~x, method="lm", se=FALSE) +
  stat_regline_equation(label.x=250, label.y=30) +
  # add style and label
  labs(
    title="Scatter Plot of MPG against Horsepower",
    subtitle="Looking at 32 cars from 'Motor Trend' magazine (1974).",
    x="horsepower (x)",
    y="miles per gallon (y)",
  )
```

:::{.notes}
This slide shows how R can be used to create nice plots in the background, without necessarily surfacing that code in the presentation itself. 
:::

## Code Output

If we roll a dice 30 times, how many threes would we expect to get?

:::{.callout-note title="Theoretical Outcome"}
The $\mathbb{P}(X=3) = \frac{1}{6}$. Therefore we expect to get $30\times\frac{1}{6} = 5$ threes.
:::

In practice, it probably won't be exactly that many.

```{r}
#| label: dice-rolls
#| echo: true
#| output-location: column

# sample space is dice face values
faces <- c(1, 2, 3, 4, 5, 6)

# roll it 30 times, allow repeats
rolls <- sample(faces, 30, replace=TRUE)

# display outcomes as a chart and a list
hist(rolls, breaks=0:6); rolls
```

:::{.notes}
On the other hand, if the code should be surfaced in the presentation (e.g. demonstrating a numerical experiment), then Quarto can do that too!
:::
